Challenges and Solutions of Developing and Implementing a Novel Desktop-as-a-Service

### 2024-05-02 paper.tex
Improved Image 1 and merged section 5 and 6

This document is structured as follows. Section~\ref{sec:relatedworkAbschnitt} discusses related work on DaaS solutions from an academic perspective, whereas section~\ref{sec:RecommendDaaSarchitecture} describes the state-of-the-art DaaS architecture DESIGN we designed and implemented. Section~\ref{sec:AnalysisPossibleComponents} presents the most relevant challenges we faced, analyses our options for handling these, and describes the solution we found. Finally, section~\ref{sec:Conclusions} discusses conclusions, and section~\ref{sec:NextSteps} includes directions for future work.

@@

@@

\begin{figure}
	\centering
	\includegraphics[width=.9\textwidth]{images/DaaS_DESIGN_Architecture_v11_english.pdf}
	\caption{Architecture of the novel DaaS DESIGN~\cite{OJCC_2023v8i1n01_Baun}.} \label{figure_architecture}
\end{figure}

@@

\section{Conclusion}
\label{sec:Conclusions}

@@

\section{Outlook}
\label{sec:NextSteps}

>>>>

This document is structured as follows. Section~\ref{sec:relatedworkAbschnitt} discusses related work on DaaS solutions from an academic perspective, whereas section~\ref{sec:RecommendDaaSarchitecture} describes the state-of-the-art DaaS architecture DESIGN we designed and implemented. Section~\ref{sec:AnalysisPossibleComponents} presents the most relevant challenges we faced, analyses our options for handling these, and describes the solution we found. Finally, section~\ref{sec:Conclusions} discusses conclusions and includes directions for future work.

@@

\begin{figure}
	\centering
	\includegraphics[width=.75\linewidth]{images/DaaS_DESIGN_Architecture_v12_english.pdf}
	\caption{Architecture of the novel DaaS DESIGN~\cite{OJCC_2023v8i1n01_Baun}.} 
	\label{figure_architecture}
\end{figure}

@@

@@

\section{Conclusion and Outlook}
\label{sec:Conclusions}

@@

% \section{Outlook}
% \label{sec:NextSteps}
